### 2014-10-31 paper/include/summary.tex
hej

\section{Summary} 
\label{sec:sum}
*conducted survey

*dram power importance

*approaches

*our ideas

Of the techniques surveyed DTail by Cui et al. stands out by showing promise for being a platform on which combining many kinds approaches is possible. Even as some of the approaches brought up in this paper shows great potential for tackling the problem with refresh power, it is important to note that they are not the only possible way. Other ways not surveyed, like scheduling of DRAM access, could also play an important role.

>>>>

\section{Summary} 
\label{sec:sum}
We have conducted a survey comprising of several proposed techniques to optimize DRAM refresh power. The survey has been performed  These techniques are based on one or several of the four approaches; Access Recency, Retention Time, Data Tolerance and Validity. DRAM refresh power is an increasing part of computing systems and to be able to mitigate this trend
